Re-fit

### 2023-01-17 scripts/r/04_refit/refit_jvc.Rmd
Fix path to processed data

cromileptes_saxatilis_durs <- read_csv(here("data", "analyses", "jvc", "cromileptes_saxatilis", "processed_data", "NF_durations.csv")) %>% 
  filter(typicality != "medium")

>>>>

cromileptes_saxatilis_durs <- read_csv(here("data", "analyses", "jvc", "cromileptes_saxatilis", "many_speech", "processed_data", "NF_durations.csv")) %>% 
  filter(typicality != "medium")
